Gender, Age, and Peer Influence on Food Incentives in Elementary Schools

### 2024-02-20 outputs/paper/paper.qmd
fixed citations

In this paper, we will provide a deeper analysis and reproduction of the paper, *Incentives and Unintended Consequences: Spillover Effects in Food Choice* (add reference). Replications of Table 1, Figures 2, and 3 were also completed from the raw data on which the original paper is based. The original study was conducted on 1631 students from various elementary schools in a low-income neighborhood in Chicago, IL, from kindergarten to grade 8. The purpose of the study was to determine whether there were spillover effects of students making decisions based on their peers' decisions as well as the incentives given to their peers. The study consisted of two stages. In the first stage (G1), each student was given a card from a deck that offered the choice of cookies or grapes, where the grapes sometimes came with a prize as an incentive to be chosen. In the second stage (G2), each student was allowed to change their choice of food based on the initial decisions of their peers. Students were sat in tables of sizes up to 10 students, in which the proportion of cards in the deck that contained incentivized grapes was 0%, 50%, or 100%. Furthermore, some tables were designated as public treatment, in which students were able to see the incentive status of their peers, and some tables were designated as private treatment, in which students were unable to see the incentive status of their peers.

>>>>

In this paper, we will provide a deeper analysis and reproduction of the paper, *Incentives and Unintended Consequences: Spillover Effects in Food Choice* [@angelucci_incentives_2019]. Replications of Table 1, Figures 2, and 3 were also completed from the raw data on which the original paper is based. The original study was conducted on 1631 students from various elementary schools in a low-income neighborhood in Chicago, IL, from kindergarten to grade 8. The purpose of the study was to determine whether there were spillover effects of students making decisions based on their peers' decisions as well as the incentives given to their peers. The study consisted of two stages. In the first stage (G1), each student was given a card from a deck that offered the choice of cookies or grapes, where the grapes sometimes came with a prize as an incentive to be chosen. In the second stage (G2), each student was allowed to change their choice of food based on the initial decisions of their peers. Students were sat in tables of sizes up to 10 students, in which the proportion of cards in the deck that contained incentivized grapes was 0%, 50%, or 100%. Furthermore, some tables were designated as public treatment, in which students were able to see the incentive status of their peers, and some tables were designated as private treatment, in which students were unable to see the incentive status of their peers.
